Evolution of the AGN UV luminosity function from redshift 7.5

### 2018-07-25 Paper/paper.tex
Update

\begin{abstract}
  Determinations of the UV luminosity function of AGN at high
  redshifts are important for constraining the AGN contribution to
  reionization and understanding the growth of supermassive black
  holes.  Recent inferences of the luminosity function suffer from
  inconsistencies arising from inhomogeneous selection and mixing of
  AGN data.  We address this problem by constructing a sample of more
  than 80,000 colour-selected AGN from redshift $z=0$ to $7.5$.  While
  this sample is composed of multiple data sets with spectroscopic
  redshifts and completeness estimates, we homogenise these data sets
  to identical cosmologies, intrinsic AGN spectra, and magnitude
  systems.  Using this sample, we derive the AGN UV luminosity
  function from redshifts $z=0$ to $7.5$.  The luminosity function has
  a double power law form at all redshifts.  The break magnitude
  brightens rapidly with redshift and the faint end of the luminosity
  function steepens.  In spite of this steepening, the contribution of
  AGN to the hydrogen photoionization rate at $z\sim 6$ is
  subdominant, although it can be non-negligible if these luminosity
  functions hold down to $M_{1450}=-18$.  Under reasonable
  assumptions, AGN can reionize \HeII\ by redshift $z=2.9$.  At low
  redshifts ($z<0.5$), AGN can produce about half of the hydrogen
  photoionization rate inferred from the statistics of \HI\ absorption
  lines in the IGM.  Our global analysis of the luminosity function
  also reveals important systematic errors in the data, particularly
  at $z=2.2$--$3.5$, which need to be addressed in future in order to
  improve our results.  We make various fitting functions, luminosity
  function analysis codes, and homogenised AGN data publicly
  available.
\end{abstract}

@@

There is a renewed interest in understanding the evolution of the UV
luminosity function of AGN, triggered by the discovery of 19
low-luminosity ($-18.9>M_{1450}>-22.6$) AGN candidates between
redshifts $z=4.1$ and $6.3$ by \citet{2015AA...578A..83G} using a
novel X-ray/NIR selection criterion.  This finding suggested that AGN
brighter than $M_{1450}\sim -18$ can account for all of the
metagalactic hydrogen photoionization rate inferred from the \lya
forest at $4<z<6$, despite the fact that these AGN are fainter than
the brightest star-forming galaxies at these redshifts.  (The UV
luminosity function of galaxies at $z=6$ has characteristic magnitude
$M^*_{1450}\sim -20$.)  A significant presence of AGN at high redshift
($z\sim 6$) and a dominant contribution of AGN to reionization is
appealing as the LyC escape fraction of galaxies is uncertain, whereas
for AGN it is close to 100\% \citep{2014ApJ...794...75S,
  2015MNRAS.449.4204L, 2016A&A...585A..48G}.  High-redshift galaxies
down to rest-frame UV magnitude $M_\mathrm{UV}=-12.5$ at $z=6$
\citep{2017ApJ...835..113L} and redshifts up to $z=11.1$
\citep{2016ApJ...819..129O} have now been reported.  But the escape of
LyC photons has been measured in only a few comparatively bright
($L>0.5L^*_\mathrm{galaxies}$) galaxies at relatively low redshifts
($z < 4$).  The escape fraction in these galaxies reveals a broad
distribution from less than 2\% to more than 80\%
\citep{2010ApJ...725.1011V, 2011ApJ...736...41B, 2015ApJ...804...17S,
  2015ApJ...810..107M, 2016A&A...585A..48G, 2017MNRAS.468..389J,
  2018arXiv180506071S, 2018arXiv180601741F, 2018arXiv180511621M,
  2018arXiv180303655C}, but the average escape fraction is typically
lower than 20\%.  Statistical constraints from \HI\ column density
measurements in gamma-ray burst (GRB) afterglow spectra suggest an
even lower escape fraction of 0.5\% \citep{2007ApJ...667L.125C,
  2009ApJS..185..526F, 2018arXiv180507318T}.  This is a challenge for
reionization models, which require an escape fraction of about 20\% in
galaxies as faint as $M_\mathrm{UV}=-13$ \citep{2016PASA...33...37F,
  2015ApJ...802L..19R, 2016MNRAS.457.4051K}.  An enhanced incidence of
high-redshift AGN may also be consistent with the shallow bright-end
slopes of the $z\sim 7$ UV luminosity function of galaxies relative to
a Schechter function \citep{2012MNRAS.426.2772B, 2014MNRAS.440.2810B,
  2014ApJ...792...76B, 2015MNRAS.452.1817B} and the hard spectra of
these galaxies \citep{2015MNRAS.450.1846S, 2015MNRAS.454.1393S,
  2017MNRAS.464..469S}.  Finally, AGN may also provide a natural
explanation for the large scatter in the \lya opacity between
different quasar sightlines close to redshift $z=6$
\citep{2015MNRAS.447.3402B, 2018arXiv180208177B}.  These opacity
fluctuations extend to substantially larger scales ($\gtrsim 50\,
h^{-1}$cMpc) than expected in galaxy-dominated reionization models
(\citealt{2015MNRAS.453.2943C}; although see
\citealt{2016MNRAS.460.1328D, 2015ApJ...813L..38D,
  2018arXiv180308932B}).  AGN clustering can result in these
fluctuations naturally if there is a significant contribution
($\gtrsim 50\%$) of AGN to the ionising emissivity at $z=5$--$6$
\citep{2017MNRAS.465.3429C}.

Several counter-arguments against a higher incidence of AGN at high
redshift have also been made. \citet{2017MNRAS.468.4691D} and
\citet{2018MNRAS.473.1416M} pointed out that an enhanced number
density of AGN at $z\sim 6$ can lead to a much earlier
\HeII\ reionization (see also \citealt{2017MNRAS.471..255K}).  For
instance, He~\textsc{ii} reionization is complete at $z=4.5$ in the
model of \citet{2015ApJ...813L...8M}, compared to $z=3$ in the
conventional scenario with sharply dropping AGN emissivity at $z>2$
\citep{2012ApJ...746..125H}.  Such early \HeII\ reionization will also
result in higher IGM temperatures due to the associated photoheating.
\citet{2017MNRAS.468.4691D} found that the temperature of the IGM at
mean density is twice as much in AGN-dominated reionization models as
the standard models at $z=3.5$--$5$, in conflict with constraints from
the \lya forest.  This inconsistency could be avoided by postulating a
reduced escape fraction of \HeII-ionizing photons in AGN, but it is
difficult to reconcile this with a unit escape fraction of
hydrogen-ionizing photons that is required to explain the Ly$\alpha$
opacity fluctuations.  Further arguments against AGN-dominated
reionization have been presented by \citet{2016MNRAS.459.2299F}, who
analysed the simulations of metal-line absorbers at $z\sim 6$.
\citet{2016MNRAS.459.2299F} find that in their cosmological radiation
hydrodynamical simulations AGN-dominated UV background results in too
many C~\textsc{iv} absorption systems relative to Si~\textsc{iv} and
C~\textsc{ii} at $z\sim 6$.  Finally, comparing the
\citet{2015AA...578A..83G} sample to X-ray-selected quasar data at
$z=0$--$6$, \citet{2017MNRAS.465.1915R} argued that the faint end of
the AGN UV luminosity function at $z\sim 6$ is probably shallower that
that reported by \citet{2015AA...578A..83G}.
\citet{2017MNRAS.465.1915R} argue that the apparent contradiction with
the results of \citet{2015AA...578A..83G} could be explained by
contamination from the host galaxies for faint AGN \citep[see
  also][]{2015MNRAS.453.1946G,2015MNRAS.448.3167W,2016MNRAS.463..348V}.

The premier way towards a more robust understanding of the AGN
contribution to the UV background is to determine the evolution of the
AGN UV luminosity function across cosmic time.  To this end, numerous
measurements of the luminosity function at various redshifts have been
published in the last decade \citep{2009A&A...507..781S,
  2011ApJ...728L..26G, 2012ApJ...755..169M, 2013ApJ...773...14R,
  2013ApJ...768..105M, 2015AA...578A..83G, 2016ApJ...833..222J,
  2016ApJ...829...33Y, 2017ApJ...847L..15O, 2018PASJ...70S..34A}.
However, many of these inferences suffer from inconsistencies arising
from inhomogeneous selection and mixing of AGN data.  Some of the data
sets analysed in these studies consist of photometric samples, which
is likely to increase sample contamination.  In some studies, distinct
data sets binned differently in redshift and magnitudes were
inhomogeneously combined.  Some authors imposed restricted priors on
parameters while fitting luminosity function models, e.g., by fixing
luminosity function slopes to certain values, which may bias the
result.  Finally, some studies arbitrarily excluded certain data sets.
This has resulted in a large scatter in the inferred high-redshift
hydrogen-ionizing AGN emissivity between various recent studies.  For
instance, there is an order of magnitude scatter between various
estimates of the hydrogen-ionizing AGN emissivity at $z=5$--$6$
\citep{2011ApJ...728L..26G, 2012ApJ...755..169M, 2015AA...578A..83G,
  2018PASJ...70S..34A, 2018AJ....155..131M, 2018MNRAS.474.2904P,
  2017ApJ...847L..15O}.  Our aim in this paper is to address this
issue, by constructing an AGN sample with robust redshift and
completeness estimates and homogeneous assumptions of the cosmology
and intrinsic AGN spectrum.  After constructing such a sample, we
derive the UV luminosity function of AGN from redshift $z=0$--$7.5$
and estimate the AGN contribution to the UV background.  We discuss
our sample construction in Section~\ref{sec:sample}.  Our derived
luminosity functions are presented in Section~\ref{sec:lf}.
Section~\ref{sec:reion} presents our inference of the AGN contribution
to the \nHI-ionizing UV background and \HeII\ reionization history.
We summarise our findings in Section~\ref{sec:conc}.

@@

We included surveys based on a set of simple criteria:
\begin{enumerate}
\item High spectroscopic completeness of the target sample.
\item Accurate rest-frame UV-optical CCD photometry.
\item Statistical power (sample size, coverage in $z$ and/or absolute magnitude).
\item A well-characterised selection function.
\end{enumerate}
As a prerequisite for a joint analysis of the QSO luminosity function
(QLF) we obtained the survey selection functions in electronic form,
either from the publication or by request from the authors. As a
reference for future surveys we make them electronically available
here in modified and homogenised form (see Section~\ref{sect:datahom}
and Appendix~\ref{sec:code}).

@@

For 2SLAQ we corrected for magnitude-dependent spectroscopic coverage
in the two survey areas \citep[$f_\mathrm{c,NGP}\left(g\right)$ and
  $f_\mathrm{c,SGP}\left(g\right)$; Figure~4
  in][]{2009MNRAS.392...19C} and spectroscopic redshift success
\citep[$f_\mathrm{s,2SLAQ}\left(g\right)$; Figure~6b
  in][]{2009MNRAS.392...19C} by multiplying them with the photometric
selection function, resulting in two area-specific 2SLAQ selection
functions
$f_\mathrm{NGP}\left(M_{1450},z\right)=f_\mathrm{p,2SLAQ}f_\mathrm{c,NGP}f_\mathrm{s,2SLAQ}$
and
$f_\mathrm{SGP}\left(M_{1450},z\right)=f_\mathrm{p,2SLAQ}f_\mathrm{c,SGP}f_\mathrm{s,2SLAQ}$
that are relevant for the QLF.  The $z<4.7$ SDSS photometric selection
function was modified to include known imaging incompleteness to
$f_{\mathrm{SDSS},z<4.7}=0.95f_{\mathrm{p,SDSS},z<4.7}$
\citep{2006AJ....131.2766R}. The BOSS colour-selected sample \citep{2013ApJ...773...14R} contains
quasars with $f_\mathrm{c,BOSS}f_\mathrm{s,BOSS}\ge 0.85$, and we adopted
$f_\mathrm{BOSS}=\overline{f_\mathrm{c,BOSS}f_\mathrm{s,BOSS}}f_\mathrm{p,BOSS}=0.962f_\mathrm{p,BOSS}$. \citet{2010ApJ...710.1498G}
presented two area-specific photometric selection functions due to
different filters employed, and more follow-up spectroscopy was
reported in \citet{2011ApJ...728L..26G}. We accounted for remaining
spectroscopic incompleteness at $R>23$, yielding the final selection
functions $f_\mathrm{NDWFS}$ and $f_\mathrm{DLS}$. The updated $z\sim
5$ SDSS photometric selection function \citep{2013ApJ...768..105M} was
modified to include imaging and spectroscopic incompleteness, yielding
$f_{\mathrm{SDSS},z\sim 5}=0.95^2f_{\mathrm{p,SDSS},z\sim 5}$. In the
deeper $z\sim 5$ SDSS Stripe~82 survey the spectroscopic
incompleteness is larger and magnitude-dependent \citep[Figure~14
  in][]{2013ApJ...768..105M}, resulting in $f_{\mathrm{S82},z\sim
  5}=0.95f_{\mathrm{s,S82},z\sim
  5}\left(i\right)f_{\mathrm{p,S82},z\sim 5}$. Likewise, imaging and
magnitude-dependent spectroscopic incompleteness was factored into the
\citet{2016ApJ...829...33Y} photometric selection function (their
Figures~5 and 7), resulting in
$f_\mathrm{SDSS+WISE}=0.97f_\mathrm{s,SDSS+WISE}\left(z_\mathrm{AB}\right)f_\mathrm{p,SDSS+WISE}$.
We obtained a rough estimate of the \citet{2015AA...578A..83G}
selection function by comparing the corrected and observed QLFs,
i.e.\ taking $f_\mathrm{GOODS-S}=\phi_\mathrm{obs}/\phi_\mathrm{corr}$
(see their Table~3).  Finally, for the three $z>6.5$ quasars we
assumed a selection function of unity in a range of $z$ and $M_{1450}$
estimated by the respective survey teams (private communication).

@@

In a magnitude bin $[M_\mathrm{min}, M_\mathrm{max})$, and redshift
  bin $[z_\mathrm{min}, z_\mathrm{max})$, we define the binned luminosity
    %% JFH Notation error here. 
function as \citep{2000MNRAS.311..433P}
\begin{equation}
  \phi \equiv \frac{N_\mathrm{QSO}}{V_\mathrm{bin}},
\end{equation}
where $N_\mathrm{QSO}$ is the number of quasars with magnitude
$M_\mathrm{min}\leq M<M_\mathrm{max}$ and redshift
$z_\mathrm{min}\leq z<z_\mathrm{max}$, and
\begin{equation}
  V_\mathrm{bin} = \int_{M_\mathrm{min}}^{M_\mathrm{max}}\mathrm{d}M
  \int_{z_\mathrm{min}}^{z_\mathrm{max}}\mathrm{d}z\, f(M, z)\,\frac{\mathrm{d}V}{\mathrm{d}z},
  \label{eqn:vi}
\end{equation}
is the effective volume of the bin. The inclusion of the survey selection function
$f(M,z)$ (Section~\ref{sect:datahom}) in Equation~(\ref{eqn:vi}) accounts for
what are sometimes called ``incomplete bins''
\citep{2006AJ....131.2766R}.  The comoving volume element $\mathrm{d}V/\mathrm{d}z$ is
given by
\begin{equation}
  \frac{\mathrm{d}V}{\mathrm{d}z}=\frac{\mathrm{d}V}{\mathrm{d}z\,\mathrm{d}\Omega}\times A\times\frac{4\pi}{41253},
\end{equation}
where $A$ is the survey area in deg$^2$, and 
\begin{equation}
  \frac{\mathrm{d}V}{\mathrm{d}z\,\mathrm{d}\Omega}=\frac{c}{H_0}\frac{d_L^2\left(z\right)}
       {\left(1+z\right)^2\left[\Omega_\mathrm{m}\left(1+z\right)^3+\Omega_\Lambda\right]^{1/2}}
  \label{eqn:dvdzdo}
\end{equation}
denotes the comoving volume element per unit solid angle
\citep{1999astro.ph..5116H}. The resulting luminosity function $\phi$ has units of
$\mathrm{cMpc}^{-3}\mathrm{mag}^{-1}$.

@@

Our estimates for the double power law luminosity function are shown
in Figure~\ref{fig:mosaic} for 25 redshift bins.  We adopt the
posterior median as our fiducial model fit, and the 68.26\%
equal-tailed credible interval as the uncertainty on $\phi$.  (We
adopt similar definitions for the derived quantities.)  The resultant
parameter values are listed in Table~\ref{tab:bins}.  Consistent with
previous studies, the double power law model provides an excellent
description of the luminosity function model over almost the complete
range of redshifts spanned by the data.  It is only in the highest
redshift bin ($z=5.5$--$6.5$) that the data seem to favour a single
power law.  In this bin, the resultant posterior distribution of the
break magnitude $M_*$ is bimodal with favoured values at the faint
($M_*>-18$) and bright end of the data ($M_*<-30$).  While in the
literature $z\sim 6$ quasars have been assumed to lie on the bright
end of the luminosity function \citep[e.g.,][]{2016ApJ...833..222J}, a
comparison with the luminosity function at lower redshifts ($z<5.5$)
suggests that these AGN should instead be understood to describe the
faint-end of a double power law.  As we discuss below, $M_*$ gets
progressively brighter with redshift.  Therefore, after inspecting the
data at lower redshifts, we use restricted priors in the
$z=5.5$--$6.5$ redshift bin in order to avoid bimodal distributions.
In this bin, we restrict the bright-end slope $\alpha$ to values less
than $-4$, which is equivalent to forcing $M_*$ to be at the bright
end of the data.  Other parameters continue to have wide uniform
priors.  This also illustrates the importance of analysing the
evolution of the QLF with redshift.

>>>>

\begin{abstract}
  Determinations of the UV luminosity function of AGN at high
  redshifts are important for constraining the AGN contribution to
  reionization and understanding the growth of supermassive black
  holes.  Recent inferences of the luminosity function suffer from
  inconsistencies arising from inhomogeneous selection and analysis of
  AGN data.  We address this problem by constructing a sample of more
  than 80,000 colour-selected AGN from redshift $z=0$ to $7.5$.  While
  this sample is composed of multiple data sets with spectroscopic
  redshifts and completeness estimates, we homogenise these data sets
  to identical cosmologies, intrinsic AGN spectra, and magnitude
  systems.  Using this sample, we derive the AGN UV luminosity
  function from redshift $z=0$ to $7.5$.  The luminosity function has
  a double power law form at all redshifts.  The break magnitude $M_*$
  of the AGN luminosity function shows a steep brightening from
  $M_*\sim -24$ at $z=0.7$ to $M_*\sim -29$ at $z=6$.  The faint-end
  slope $\beta$ significantly steepens from $-1.7$ at $z<2.2$ to
  $-2.4$ at $z\simeq 6$.  In spite of this steepening, the
  contribution of AGN to the hydrogen photoionization rate at $z\sim
  6$ is subdominant ($<3$\%), although it can be non-negligible ($\sim
  10$\%) if these luminosity functions hold down to $M_{1450}=-18$.
  Under reasonable assumptions, AGN can reionize \HeII\ by redshift
  $z=2.9$.  At low redshifts ($z<0.5$), AGN can produce about half of
  the hydrogen photoionization rate inferred from the statistics of
  \HI\ absorption lines in the IGM.  Our global analysis of the
  luminosity function also reveals important systematic errors in the
  data, particularly at $z=2.2$--$3.5$, which need to be addressed and
  incorporated in the AGN selection function in future in order to
  improve our results.  We make various fitting functions, luminosity
  function analysis codes, and homogenised AGN data publicly
  available.
\end{abstract}

@@

There is a renewed interest in understanding the evolution of the UV
luminosity function of AGN, triggered by the discovery of 19
low-luminosity ($-18.9>M_{1450}>-22.6$) AGN candidates between
redshifts $z=4.1$ and $6.3$ by \citet{2015AA...578A..83G} using a
novel X-ray/NIR selection criterion.  This finding suggested that AGN
brighter than $M_{1450}\sim -18$ can account for all of the
metagalactic hydrogen photoionization rate inferred from the \lya
forest at $4<z<6$, despite the fact that these AGN are fainter than
the brightest star-forming galaxies at these redshifts.  (The UV
luminosity function of galaxies at $z=6$ has characteristic magnitude
$M^*_{1450}\sim -20$ \citep{2015ApJ...803...34B}.)  A significant
presence of AGN at high redshift ($z\sim 6$) and a dominant
contribution of AGN to reionization is appealing as the LyC escape
fraction of galaxies is uncertain, whereas for AGN it is close to
100\% \citep{2014ApJ...794...75S, 2015MNRAS.449.4204L,
  2016A&A...585A..48G}.  High-redshift galaxies down to rest-frame UV
magnitude $M_\mathrm{UV}=-12.5$ at $z=6$ \citep{2017ApJ...835..113L}
and redshifts up to $z=11.1$ \citep{2016ApJ...819..129O} have now been
reported.  But the escape of LyC photons has been measured in only a
few comparatively bright ($L>0.5L^*_\mathrm{galaxies}$) galaxies at
relatively low redshifts ($z < 4$).  The escape fraction in these
galaxies reveals a broad distribution from less than 2\% to more than
80\% \citep{2010ApJ...725.1011V, 2014Sci...346..216B,
  2015ApJ...810..107M, 2016A&A...585A..48G, 2016Natur.529..178I,
  2016ApJ...826L..24S, 2017MNRAS.468..389J, 2018arXiv180506071S,
  2018arXiv180601741F, 2018arXiv180511621M, 2018arXiv180303655C,
  2018MNRAS.478.4851I, 2018MNRAS.474.4514I}, but the average escape
fraction is typically lower than 20\%.  Statistical constraints from
\HI\ column density measurements in gamma-ray burst (GRB) afterglow
spectra suggest an even lower escape fraction of 0.5\%
\citep{2007ApJ...667L.125C, 2009ApJS..185..526F, 2018arXiv180507318T}.
This is a challenge for reionization models, which require an escape
fraction of about 20\% in galaxies as faint as $M_\mathrm{UV}=-13$
\citep{2016PASA...33...37F, 2015ApJ...802L..19R, 2016MNRAS.457.4051K}.
An enhanced incidence of high-redshift AGN may also be consistent with
the shallow bright-end slopes of the $z\sim 7$ UV luminosity function
of galaxies relative to a Schechter function
\citep{2012MNRAS.426.2772B, 2014MNRAS.440.2810B, 2014ApJ...792...76B,
  2015MNRAS.452.1817B} and the hard spectra of these galaxies
\citep{2015MNRAS.450.1846S, 2015MNRAS.454.1393S, 2017MNRAS.464..469S,
  2017ApJ...851...40L}.  Finally, AGN may also provide a natural
explanation for the large scatter in the \lya opacity between
different quasar sightlines close to redshift $z=6$
\citep{2015MNRAS.447.3402B, 2018arXiv180208177B, 2018arXiv180704229E}.
These opacity fluctuations extend to substantially larger scales
($\gtrsim 50\, h^{-1}$cMpc) than expected in galaxy-dominated
reionization models (\citealt{2015MNRAS.453.2943C}; although see
\citealt{2016MNRAS.460.1328D, 2015ApJ...813L..38D,
  2018arXiv180308932B}).  AGN clustering can result in these
fluctuations naturally if there is a significant contribution
($\gtrsim 50\%$) of AGN to the ionising emissivity at $z=5$--$6$
\citep{2017MNRAS.465.3429C}.

Several counter-arguments against a higher incidence of AGN at high
redshift have also been made. \citet{2017MNRAS.468.4691D} and
\citet{2018MNRAS.473.1416M} pointed out that an enhanced number
density of AGN at $z\sim 6$ can lead to a \HeII\ reionization that
occurs much earlier than indicated by the observed evolution of
\HeII\ IGM opacity \citep{2011ApJ...733L..24W, 2016ApJ...825..144W}
and the evolution of the IGM temperature \citep{2011MNRAS.410.1096B,
  2014MNRAS.441.1916B} (see also \citealt{2017MNRAS.471..255K}).  For
instance, He~\textsc{ii} reionization is complete at $z=4.5$ in the
model of \citet{2015ApJ...813L...8M}, compared to $z=3$ in the
conventional scenario with sharply dropping AGN emissivity at $z>2$
\citep{2012ApJ...746..125H}.  Such early \HeII\ reionization will also
result in higher IGM temperatures due to the associated photoheating.
\citet{2017MNRAS.468.4691D} found that the temperature of the IGM at
mean density is twice as much in AGN-dominated reionization models as
the standard models at $z=3.5$--$5$, in conflict with constraints from
the \lya forest.  This inconsistency could be avoided by postulating a
reduced escape fraction of \HeII-ionizing photons in AGN, but it is
difficult to reconcile this with a unit escape fraction of
hydrogen-ionizing photons that is required to explain the Ly$\alpha$
opacity fluctuations.  Further arguments against AGN-dominated
reionization have been presented by \citet{2016MNRAS.459.2299F}, who
analysed the simulations of metal-line absorbers at $z\sim 6$.
\citet{2016MNRAS.459.2299F} find that in their cosmological radiation
hydrodynamical simulations AGN-dominated UV background results in too
many C~\textsc{iv} absorption systems relative to Si~\textsc{iv} and
C~\textsc{ii} at $z\sim 6$.  Finally, comparing the
\citet{2015AA...578A..83G} sample to X-ray-selected quasar data at
$z=0$--$6$, \citet{2017MNRAS.465.1915R} argued that the faint end of
the AGN UV luminosity function at $z\sim 6$ is probably shallower that
reported by \citet{2015AA...578A..83G}.  \citet{2017MNRAS.465.1915R}
argue that the apparent contradiction with the results of
\citet{2015AA...578A..83G} could be explained by contamination from
the host galaxies for faint AGN \citep[see
  also][]{2015MNRAS.453.1946G,2015MNRAS.448.3167W,2016MNRAS.463..348V}.

The premier way towards a more robust understanding of the AGN
contribution to the UV background is to determine the evolution of the
AGN UV luminosity function across cosmic time.  To this end, numerous
measurements of the luminosity function at various redshifts have been
published in the last decade \citep{2009A&A...507..781S,
  2009MNRAS.392...19C, 2010AJ....139..906W, 2011ApJ...728L..26G,
  2012ApJ...755..169M, 2013ApJ...773...14R, 2013ApJ...768..105M,
  2015AA...578A..83G, 2016ApJ...833..222J, 2016ApJ...829...33Y,
  2016A&A...587A..41P, 2017ApJ...847L..15O, 2018PASJ...70S..34A,
  2018AJ....155..131M}.  However, many of these inferences suffer from
inconsistencies arising from inhomogeneous selection and analysis of AGN
data.  Some of the data sets analysed in these studies consist of
photometric samples, which is likely to increase sample contamination.
In some studies, distinct data sets binned differently in redshift and
magnitudes were inhomogeneously combined.  Some authors imposed
restricted priors on parameters while fitting luminosity function
models, e.g., by fixing luminosity function slopes to certain values,
which may bias the result.  Finally, some studies arbitrarily excluded
certain data sets.  This has resulted in a large scatter in the
inferred high-redshift hydrogen-ionizing AGN emissivity between
various recent studies.  For instance, there is an order of magnitude
scatter between various estimates of the hydrogen-ionizing AGN
emissivity at $z=5$--$6$ \citep{2011ApJ...728L..26G,
  2012ApJ...755..169M, 2015AA...578A..83G, 2018PASJ...70S..34A,
  2018AJ....155..131M, 2018MNRAS.474.2904P, 2017ApJ...847L..15O}.  Our
aim in this paper is to address this issue, by constructing an AGN
sample with robust redshift and completeness estimates and homogeneous
assumptions of the cosmology and intrinsic AGN spectrum.  After
constructing such a sample, we derive the UV luminosity function of
AGN from redshift $z=0$--$7.5$ and estimate the AGN contribution to
the UV background.  We discuss our sample construction in
Section~\ref{sec:sample}.  Our derived luminosity functions are
presented in Section~\ref{sec:lf}.  Section~\ref{sec:reion} presents
our inference of the AGN contribution to the \nHI-ionizing UV
background and \HeII\ reionization history.  We summarise our findings
in Section~\ref{sec:conc}.

@@

We included surveys based on a set of simple criteria:
\begin{enumerate}
\item High spectroscopic completeness of the target sample.
\item Accurate rest-frame UV-optical CCD photometry.
\item Statistical power (sample size, coverage in $z$ and/or absolute magnitude).
\item A well-characterised selection function.
\end{enumerate}
As a prerequisite for a joint analysis of the QSO luminosity function
(QLF) we obtained the survey selection functions in electronic form,
either from the publication or by request from the authors. As a
reference for future surveys we make them electronically available
here in modified and homogenised form (see Section~\ref{sect:datahom}
and Appendix~\ref{sec:code})\footnote{These data and the code for
  deriving the luminosity functions are available on
  \url{https://github.com/gkulkarni/QLF}.  The data will also be made
  available on CDS upon acceptance of this manuscript for
  publication.}.

@@

For 2SLAQ we corrected for magnitude-dependent spectroscopic coverage
in the two survey areas \citep[$f_\mathrm{c,NGP}\left(g\right)$ and
  $f_\mathrm{c,SGP}\left(g\right)$; Figure~4
  in][]{2009MNRAS.392...19C} and spectroscopic redshift success
\citep[$f_\mathrm{s,2SLAQ}\left(g\right)$; Figure~6b
  in][]{2009MNRAS.392...19C} by multiplying them with the photometric
selection function, resulting in two area-specific 2SLAQ selection
functions
$f_\mathrm{NGP}\left(M_{1450},z\right)=f_\mathrm{p,2SLAQ}f_\mathrm{c,NGP}f_\mathrm{s,2SLAQ}$
and
$f_\mathrm{SGP}\left(M_{1450},z\right)=f_\mathrm{p,2SLAQ}f_\mathrm{c,SGP}f_\mathrm{s,2SLAQ}$
that are relevant for the QLF.  The $z<4.7$ SDSS photometric selection
function was modified to include known imaging incompleteness to
$f_{\mathrm{SDSS},z<4.7}=0.95f_{\mathrm{p,SDSS},z<4.7}$
\citep{2006AJ....131.2766R}. The BOSS colour-selected sample
\citep{2013ApJ...773...14R} contains quasars with
$f_\mathrm{c,BOSS}f_\mathrm{s,BOSS}\ge 0.85$, and we adopted
$f_\mathrm{BOSS}=\overline{f_\mathrm{c,BOSS}f_\mathrm{s,BOSS}}
f_\mathrm{p,BOSS}=0.962f_\mathrm{p,BOSS}$. \citet{2010ApJ...710.1498G}
presented two area-specific photometric selection functions due to
different filters employed, and more follow-up spectroscopy was
reported in \citet{2011ApJ...728L..26G}. We accounted for remaining
spectroscopic incompleteness at $R>23$, yielding the final selection
functions $f_\mathrm{NDWFS}$ and $f_\mathrm{DLS}$. The updated $z\sim
5$ SDSS photometric selection function \citep{2013ApJ...768..105M} was
modified to include imaging and spectroscopic incompleteness, yielding
$f_{\mathrm{SDSS},z\sim 5}=0.95^2f_{\mathrm{p,SDSS},z\sim 5}$. In the
deeper $z\sim 5$ SDSS Stripe~82 survey the spectroscopic
incompleteness is larger and magnitude-dependent \citep[Figure~14
  in][]{2013ApJ...768..105M}, resulting in $f_{\mathrm{S82},z\sim
  5}=0.95f_{\mathrm{s,S82},z\sim
  5}\left(i\right)f_{\mathrm{p,S82},z\sim 5}$. Likewise, imaging and
magnitude-dependent spectroscopic incompleteness was factored into the
\citet{2016ApJ...829...33Y} photometric selection function (their
Figures~5 and 7), resulting in
$f_\mathrm{SDSS+WISE}=0.97f_\mathrm{s,SDSS+WISE}
\left(z_\mathrm{AB}\right)f_\mathrm{p,SDSS+WISE}$.  We obtained a
rough estimate of the \citet{2015AA...578A..83G} selection function by
comparing the corrected and observed QLFs, i.e.\ taking
$f_\mathrm{GOODS-S}=\phi_\mathrm{obs}/\phi_\mathrm{corr}$ (see their
Table~3).  Finally, for the three $z>6.5$ quasars we assumed a
selection function of unity in a range of $z$ and $M_{1450}$ estimated
by the respective survey teams (private communication).

@@

In a magnitude bin $[M_\mathrm{min}, M_\mathrm{max})$, and redshift
  bin $[z_\mathrm{min}, z_\mathrm{max})$, we define the binned luminosity
function as \citep{2000MNRAS.311..433P}
\begin{equation}
  \phi \equiv \frac{N_\mathrm{QSO}}{V_\mathrm{bin}},
\end{equation}
where $N_\mathrm{QSO}$ is the number of quasars with magnitude
$M_\mathrm{min}\leq M<M_\mathrm{max}$ and redshift
$z_\mathrm{min}\leq z<z_\mathrm{max}$, and
\begin{equation}
  V_\mathrm{bin} = \int_{M_\mathrm{min}}^{M_\mathrm{max}}\mathrm{d}M
  \int_{z_\mathrm{min}}^{z_\mathrm{max}}\mathrm{d}z\, f(M, z)\,\frac{\mathrm{d}V}{\mathrm{d}z},
  \label{eqn:vi}
\end{equation}
is the effective volume of the bin. The inclusion of the survey selection function
$f(M,z)$ (Section~\ref{sect:datahom}) in Equation~(\ref{eqn:vi}) accounts for
what are sometimes called ``incomplete bins''
\citep{2006AJ....131.2766R}.  The comoving volume element $\mathrm{d}V/\mathrm{d}z$ is
given by
\begin{equation}
  \frac{\mathrm{d}V}{\mathrm{d}z}=\frac{\mathrm{d}V}{\mathrm{d}z\,\mathrm{d}\Omega}\times A\times\frac{4\pi}{41253},
\end{equation}
where $A$ is the survey area in deg$^2$, and 
\begin{equation}
  \frac{\mathrm{d}V}{\mathrm{d}z\,\mathrm{d}\Omega}=\frac{c}{H_0}\frac{d_L^2\left(z\right)}
       {\left(1+z\right)^2\left[\Omega_\mathrm{m}\left(1+z\right)^3+\Omega_\Lambda\right]^{1/2}}
  \label{eqn:dvdzdo}
\end{equation}
denotes the comoving volume element per unit solid angle
\citep{1999astro.ph..5116H}. The resulting luminosity function $\phi$ has units of
$\mathrm{cMpc}^{-3}\mathrm{mag}^{-1}$.

@@

Our estimates for the double power law luminosity function are shown
in Figure~\ref{fig:mosaic} for 25 redshift bins.  We adopt the
posterior median as our fiducial model fit, and the 68.26\%
equal-tailed credible interval as the uncertainty on $\phi$.  (We
adopt similar definitions for the derived quantities.)  The resultant
parameter values are listed in Table~\ref{tab:bins}.\footnote{Full
  posterior distributions for the luminosity functions themselves
  should be obtained by running our publicly available code.  This is
  also true for other models and derived quantities such as
  emissivities that we discuss in this paper.} Consistent with
previous studies, the double power law model provides an excellent
description of the luminosity function model over almost the complete
range of redshifts spanned by the data.  It is only in the highest
redshift bin ($z=5.5$--$6.5$) that the data seem to favour a single
power law.  In this bin, the resultant posterior distribution of the
break magnitude $M_*$ is bimodal with favoured values at the faint
($M_*>-18$) and bright end of the data ($M_*<-30$).  While in the
literature $z\sim 6$ quasars have been assumed to lie on the bright
end of the luminosity function \citep[e.g.,][]{2016ApJ...833..222J}, a
comparison with the luminosity function at lower redshifts ($z<5.5$)
suggests that these AGN should instead be understood to describe the
faint-end of a double power law.  As we discuss below, $M_*$ gets
progressively brighter with redshift.  Therefore, after inspecting the
data at lower redshifts, we use restricted priors in the
$z=5.5$--$6.5$ redshift bin in order to avoid bimodal distributions.
In this bin, we restrict the bright-end slope $\alpha$ to values less
than $-4$, which is equivalent to forcing $M_*$ to be at the bright
end of the data.  Other parameters continue to have wide uniform
priors.  This also illustrates the importance of analysing the
evolution of the QLF with redshift.
